\sysfull

### 2017-08-10 paper/evaluation.tex
commented out section about batery-less FFT

\subsubsection{Case Study}
\label{sec:case_study}

The final experiment assessing usefulness of \sys's use in real application. For this we have a implemented an battery-less wirelessly-powered sound detector as an example. To the best of our knowledge, this is the first case study that demonstrates a intermittently-powered system supplied by harvested energy at runtime, which continuously interacts with real-life signals.

The application aims at detecting a specific tone in the audio signal (in the implementation: 1\,kHz) based on on-the-fly audio measurement. For this we have connected an analog MEMS microphone~\cite{microphone} output to AUX3 port of WISP\,5.1 (while the microphone was powered directly by WISP, which was then wirelessly power-supplied by the RFID reader). Audio signal is sampled by the microcontroller's ADC and passed to the FFT function (internal function of the TI's Digital Signal Processing library~\cite{ti_dsp}) to find a tone above a predefined threshold. The output of the detection is signalled by the WISP on-board LED. The video of demonstrating the working system is available via \url{https://link_to_a_video}.

Expected results:
\begin{itemize}
	\item Compare execution time: \sys against Chain for X\,s long audio signal detection at two antenna distances
	\item Make a video of the demonstration 
\end{itemize}

\todo{Check if we really need this application}{Brandon}
\todo{Provide results and text to this section---if time allows (this result is not critical)}{Amjad/Przemek}

>>>>

%\subsubsection{Case Study}
%\label{sec:case_study}

%The final experiment assessing usefulness of \sys's use in real application. For this we have a implemented an battery-less wirelessly-powered sound detector as an example. To the best of our knowledge, this is the first case study that demonstrates a intermittently-powered system supplied by harvested energy at runtime, which continuously interacts with real-life signals.

%The application aims at detecting a specific tone in the audio signal (in the implementation: 1\,kHz) based on on-the-fly audio measurement. For this we have connected an analog MEMS microphone~\cite{microphone} output to AUX3 port of WISP\,5.1 (while the microphone was powered directly by WISP, which was then wirelessly power-supplied by the RFID reader). Audio signal is sampled by the microcontroller's ADC and passed to the FFT function (internal function of the TI's Digital Signal Processing library~\cite{ti_dsp}) to find a tone above a predefined threshold. The output of the detection is signalled by the WISP on-board LED. The video of demonstrating the working system is available via \url{https://link_to_a_video}.

%Expected results:
%\begin{itemize}
%	\item Compare execution time: \sys against Chain for X\,s long audio signal detection at two antenna distances
%	\item Make a video of the demonstration 
%\end{itemize}

%\todo{Check if we really need this application}{Brandon}
%\todo{Provide results and text to this section---if time allows (this result is not critical)}{Amjad/Przemek}
